A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-09-14 docs/results_JAMwithSB_v1.01.tex
Wrote section on future work and removed some TO DOs.

\paragraph{... with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_{I,\text{tot}}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The "best" fit is $\Upsilon_{I,*}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

@@

\paragraph{... with Increasing Mass-to-Light Ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot},i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot},i} L_i$. We treat the five $\Upsilon_{\text{I,tot},i}$ as free parameters and only require that $\Upsilon_{\text{I,tot},j} \geq \Upsilon_{\text{I,tot},i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$. The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????]. The strong rise of $\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really??? Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec. The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise. A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF]. The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Enclosed mass and mass-to-light ratio profile. [TO DO: Make figure wider. Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes. It's better to have ML on the left side, to read up the central ML.] [TO DO: local mass to light ratio $\Upsilon_\text{I,tot}(R')$]}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{tot}$ profile used to generate a mass model from the light distribution.  This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line). \emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and mass-to-light profile $\Upsilon(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model. The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line). The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars). The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio. Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
\label{fig:modelG}
\end{figure*}

>>>>

\paragraph{... with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

@@

\paragraph{... with Increasing Mass-to-Light Ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$. We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$. The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????]. The strong rise of $\Upsilon_\text{I,tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_\text{i,*}$ alone [TO DO: Really??? Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec. The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise. A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF]. The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Enclosed mass and mass-to-light ratio profile. [TO DO: Make figure wider. Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes. It's better to have ML on the left side, to read up the central ML.] [TO DO: local mass to light ratio $\Upsilon_\text{I,tot}(R')$]}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{I,tot}(R')$ profile used to generate a mass model from the light distribution.  This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line). \emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model. The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line). The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars). The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio. Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
\label{fig:modelG}
\end{figure*}

### 2015-09-14 docs/results_lensing_v1.02.tex
Finished discussion on stellar mass-to-light ratios.
Wrote section on future work and removed some TO DOs.

\begin{table}
\centering
\begin{minipage}{70mm}
\begin{tabular}{r|rrrr|c}
\hline
  & A & B & C & D & G\\\hline
$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
\hline
\end{tabular}
\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}. The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}. The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel. \textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here. Should I change this table and the error bars in the figures to match this bug????}}
\label{tab:lenspos}
\end{minipage}
\end{table}

@@

\begin{table*}
\centering
\caption{[TO DO: Caption] ??? in Table \ref{tab:lenspos}, for $\alpha = 1$}
\begin{tabular}{llrrclr}
\hline
 &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
 &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
Einstein radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
Source position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
\end{tabular}  
\label{tab:bestfitlensmodel} 
\end{table*}

@@

\paragraph{Comparison with Light Distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius. Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g. an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.  We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

@@

\begin{table}
\centering
\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$. $R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table}

@@

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution. [TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Predicted mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours). To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein}$ in Table \ref{tab:einsteinML}. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
\label{fig:lenslightcompareALL}
\end{figure*}

>>>>

\begin{table}
\centering
\begin{minipage}{70mm}
\begin{tabular}{r|rrrr|c}
\hline
  & A & B & C & D & G\\\hline
$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
\hline
\end{tabular}
\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}. The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}. The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.}
\label{tab:lenspos}
\end{minipage}
\end{table}

@@

\begin{table*}
\centering
\caption{Best fit lens model found from the peak image positions in Table \ref{tab:lenspos} (first column) following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$). The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions (column 2).}
\begin{tabular}{llrrclr}
\hline
 &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
 &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
Einstein radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
Source position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
\end{tabular}  
\label{tab:bestfitlensmodel} 
\end{table*}

@@

\paragraph{Comparison with Light Distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius. Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g. an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.  We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

@@

\begin{table*}
\centering
\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$. $R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table*}

@@

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Predicted mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours). To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein}$ in Table \ref{tab:einsteinML}. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible. [TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
\label{fig:lenslightcompareALL}
\end{figure*}
